---
title: "Tutorial"
author: "Raphael Fredebeul"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
This vignette will introduce my package 'softdev' which is part of the course bulding R-Packages by the Coursera specialization 'Mastering Software Development in R'. The functions provided for you in this package will be using data from the US National Highway Traffic Safety Administration's Fatality Analysis Reporting System, which is a nationwide census providing the American public yearly data regarding fatal injuries suffered in motor vehicle traffic crashes. In order to present the usage of the functions. We will go through them step-by-step.
## make_filename
This function constructs a filename that is used as input for other functions, e.g. fars_read()
```{r}
library(softdev)
file <- make_filename(2015)
file
```

## fars_read()
This function reads a csv file if existant and creates a data frame tbl. In our case if we want to read the data for the year 2015, the code would be:
```{r }
data <- fars_read(file)
```
## fars_read_years()
This function returns the observation "month" and "year" for a list of datasets.
```{r warning=FALSE}
data <- fars_read_years(c(2013,2015))
```
## fars_summarize_years()
This function returns a tibble that summarizes the number of observations for each month and each dataset.
```{r warning=FALSE}
library(dplyr)
fars_summarize_years(c(2013,2015))
```
## fars_map_state()
This function plots the occurence of fatal injuries suffered in motor vehicle traffic crashes.
```{r}
fars_map_state(50, 2013)
```

